A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-06-26 paper/elsarticle/elsarticle-template.tex
paper

\paragraph{Virtual projector}

@@

A natural extension of this work would be to address non-planar scenes. To handle non-planar scenes would call for a change in how scene geometry is recovered and how distortion of the image to be projected is carried out; projector calibration---presented here as a one-time step---could, however, remain unchanged.

>>>>

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected. This placement is produced according to a small handful of steps. First, we (i) intersect the scene plane with the optical axis (i.e., the ray from the projector's center of projection through the center of the image plane); next, we (ii) rotate the projector's placement about that point of intersection, aligning it with the scene plane's normal vector and giving an initial virtual projector. Separately, we (iii) carry out steps (i) and (ii) for the camera, giving a virtual camera likewise facing directly downwards to the scene plane. Finally, we (iv) rotate the $X$- and $Y$-axes of the initial virtual projector with those of the virtual camera, which gives the virtual projector. The virtual projector is thus rendered fronto-parallel with the scene plane, enabling projection to the scene plane absent of projective distortions. Moreover, the virtual projector's axes are aligned with the axes of an image of the scene acquired by a camera, enabling intuitive placement of augmentations in the scene.

@@

A natural extension of this work would be to address non-planar scenes. To handle non-planar scenes would call for a change in how scene geometry is recovered and how distortion of the image to be projected is carried out; projector calibration could, however, be left unchanged.
